\section{Database}
\label{sect:database}
As ProGENitor needed a method to pull large amounts of data off the backend
server database, a Java method had to be implemented that interfaced with
the database.  MySQL was chosen as it is open source, widely used, and fairly
easy to quickly learn.  Once the MySQL interface was established a wrapper was
added such that another database method could be inserted without a significant
work effort in the rest of the code.  Then, through this wrapper, the many
different function calls were implemented to collect the data needed to generate
the career map and derive any further insights through Weka.

\subsection{MySQL Interface}
To greatly simplify this work, a predefined library jar was added
to the project.  In this case, the library used was SQLite JDBC.  The SQLite
library allows for easy access to a MySQL database for creating, reading from,
writing to, and querying the database.  In the case of ProGENitor, once the
library was added, the code was very straight forward.  Through a couple
commands, the code established the database connection, ran the specified query
or other command, and collected the returned data.\cite{sqlite}  Using the
SQLite library allowed the MySQL interface to quickly add in functions to create
a database, collect query matches from the database, upload lines and files to
the database, modify lines within the database, and even pull the entire
database.  With these functions in place, ProGENitor easily and quickly can
access any defined database.  In the case of ProGENitor, four databases were
generated; one for user profile data, one for education data, one for job data,
and finally one that contains the headers of the other databases.  If, in the
future, additional databases are needed, ProGENitor can easily add them. 
Additionally, as the SQL commands are standard commands, the interface can
easily be replaced with another database interface or expanded upon by anyone
familiar with a SQL language.

\subsection{User Wrapper}
As previously stated, it was desired that ProGENitor be setup such that it was
easy to swap out the database interface with another interface.  Thus, the user
interface wrapper was written to call the various SQL commands.  If in the
future, the database needed to be changed, the work to do so would reside in
adding the database interface and changing the user interface wrapper to point
to the new database.  The wrapper also adds in commands that make interfacing
with the code a bit more clear.  Commands such as add user, database
setup, query matching users, and return headers all allow users working through
other portions of code to understand what the function calls are actually doing
and do not require the developer to necessarily understand the database
interface commands.  Then using these commands, ProGENitor can then collect
data that it passes along to be interpreted by the connections and insights
packages.

\subsection{Data Collection}
With the wrapper and SQL interface in place, ProGENitor then implements a couple
different calls to gather data to be analyzed.  The first of these calls is find
same, in which the code polls the data base for all users that match the query
field value passed to the method.  This method then returns the user IDs in a
TreeSet for all of the users that matched the query.  The next data collection
method available, find all node data, does the same function, but instead
returns all of the matching data in an ArrayList.  The final data collection method available,
database pull, returns in an ArrayList, all of the data associated with the
TreeSet of IDs passed to the method.  These methods are all very similar, but
allow for easy data collection by the mapping and Weka methods within the
connections and insights packages.
