\section{Synthetic Data}
\label{sect:mock-data}
As most end user's databases are not easily accessible and having control over
the data in databases allows for better testing, generating synthetic data that
is then loaded into a local database was chosen for ProGENitor development. 
ProGENitor is easily attached to any other databases, so this only speeds up the
development process.  To generate this data, a script was written that
consumes various data files containing possible data values and then randomly
selects from these values to populate the database.  The number of users
generated and other variables are also controllable within the script.  Once the
script completes it outputs a file containing all of the user data, which can
then be uploaded to the database through the database architecture included with
ProGENitor.

\subsection{Data Files}
To allow for easily updatable synthetic data, separate data files were
implemented.  This was done so that the values weren't embedded deep within the
data generation code.  There are two different types of data files.  The first type simply contains a list
of all possible values.  These values are then simply loaded into an array by
the data generation script.  Then, the script randomly selects from the
array when it needs one of these values.  The second type contains a listing of
possible values dependant on a previous value.  For example, in the line below,
to get a Master's Degree in Circuits or Computer Systems, the user must first
obtain a Bachelor's Degree in Electrical.
\begin{footnotesize}
\\*\begin{tt}
\\*Electrical:Circuits,Computer Systems\\*
\\*\end{tt}
\end{footnotesize}
Thus, the code will search the second file type for the line that meets the
dependency.  Once the line is found, it will load the possible values into an
array and then randomly select from one of these values.

\subsection{Random Selection}
There are two places the code must randomly select data.  The first is the
data that is loaded for each vertex.  This random selection simply places the data
from one of the data files into an array and uses a standard random function
to randomly select an array index value to pull the data from.  This data is then
applied to the individual user's vertex.  When the vertex has all necessary data
generated, it is loaded into the data file to be loaded into the database.  In
testing, to force a particular piece of data to occur more frequently,
simply placing it multiple times into the data files will increase the
frequency that it will show up in the user data.

The second place that code must randomly select data is when it is determining
if a user enters a vertex or not on each pass.  There are four possible types
of vertices that a user could enter during each loop.  In each pass of the loop,
they could potentially enter up to all of the vertices.  These vertices are an
undergraduate degree, a master's degree, a PhD, and a job.  For each of these
vertices, a chance value is assigned in the variables at the top of the script. 
Then essentially a ten sided dice is rolled at each vertex, this is done by
loading values 1 through 10 into an array and applying the standard random
function to the array.  If the dice roll is greater than the predefined chance
variable value, the vertex is entered and data is generated.  When any vertex is
entered, all educational chance variable values are incremented by 1.  This
means it is much less likely someone will get an advanced degree as their career
progresses.  Additionally, each educational degree level is currently limited to
one degree and requires the previous level have been completed.  All of these
variables are adjustable in the code; so many different scenarios can be generated.


\subsection{Code Flow}
Once the data files and random data selection is understood, the code flow is
relatively straight forward.  The code steps through the data, section by
section, generating data for each user and then stores it in a data file that
can later be uploaded into the database.  Figure \ref {fig:data generation}
depicts this process.

\pagebreak
\usetikzlibrary{shapes,arrows,chains}

\begin{figure}[H]
	\centering
% Start the picture
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=6mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=15em},
  test/.style={base, diamond, aspect=5, text width=10em},
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [proc] (p0) {Initialize Tunable Variables, pull in
data files};
% Use join to connect a node to the previous one 
\node [proc, join] (p1) {Increment ID}; 
\node [proc, join] (p2) {Generate User Profile Data};
\node [proc, join] (p3) {Calculate Years left in workforce/higher education};
\node [test, join] (t0) {If UG, generate random bachelor's degree};
\node [test, join] (t1) {If MS, generate random master's degree};
\node [test, join] (t2) {If PhD, generate random PhD information};
\node [test, join] (t3) {If Job, generate random job information};
\node [proc, join] (p4) {Store User Information to Data File};

\draw [->, dotted, thick, shorten >=1mm] (t3.south) -- ++(40mm,-5mm)  --
++(27mm,0) |- node [black, near end, yshift=0.75em, xshift=5mm, it]
    [above]{While time remaining}(p3);
    
\draw [->, dotted, thick, shorten >=1mm] (t3.south) -- ++(40mm,-5mm)  --
++(27mm,0) |- node [black, near end, yshift=0.75em, xshift=-2mm, it]
    {in workforce}(p3);

\draw [->, dotted, thick, shorten >=1mm]
  (p4.south) -- ++(50mm,-5mm)  -- ++(27mm,0) 
  |- node [black, near end, yshift=0.75em, xshift=5mm,  it]
    {Until User ID = \# Users} (p1);

% -------------------------------------------------
\end{tikzpicture}
	\caption{High Level Data Generation}
	\label{fig:data generation}
\end{figure}