\section{High Level Architecture}
\label{sect:high-level-architecture}
ProGENitor is broken into several different pieces of code.  To place a call
to ProGENitor, the user must send a query and a query type when starting the
application.  This query is typically a job title that the user wishes to reach.
The query is then passed to the database block which will fetch data from the
database.  The data in the database is loaded with synthetic data for testing
purposes, but could easily be replaced with an actual database. The fetched data
would then be passed to a block of code, that processes the data to produce a
career path graph and then extracts the significant information about the graph
points.  Additional information is also extracted by a tool called Weka, to
provide more complex insights into the combinations of data points that may be
relevant to reaching the queried goal.  This data is then returned to the user
in a data object that can be rendered by a user interface.  See Figure \ref{fig:HighLevelProjectArchitecture}
for a representation of this sequence.

\usetikzlibrary{shapes,arrows,chains}

\begin{figure}[H]
	\centering
  	\resizebox {!} {20mm} {
% Start the picture
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=3mm and 20mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=2ex},
  node/.style={base, circle, text width=5em},
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw},
  thin/.style={->,>=stealth',shorten >=1pt, black},
  nm/.style={->,>=stealth',shorten >=1pt, green},
  to/.style={->,>=stealth',shorten >=1pt,semithick,blue},
  thick/.style={->,shorten >=1pt,very thick, red},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [node, join, xshift=-30mm] (a) {Synthetic Data};
\node [node, join, right = of a, xshift=8mm] (b) {Database};
\node [node, join, right = of b, xshift=12mm] (c) {Data Fetch}; 
\node [node, join, right = of c, xshift=10mm] (d) {Career Path Graph \& Weka};
\node [node, join, right = of d, xshift=10mm] (e) {Data Return};

\draw [->](c.west) |- node {} (b);

% -------------------------------------------------
\end{tikzpicture}
}

	\caption{High Level Architecture}
	\label{fig:HighLevelProjectArchitecture}
\end{figure}

\subsection{Overall Technology Stack}
All of the code for ProGENitor is written in Java except for the synthetic data
generation code which is written in Perl.  Java was selected because the code
needed to interface well with web applications and pages.  Java is easily run through
web interfaces and can easily pass data by passing JSON \cite{json} Objects. 
Additionally, Java interfaces well with databases.  As this project does a lot of database
scraping this was very important.
